---
title: "CODEBOOK"
author: "Tingting"
date: "7 5 2019"
output: html_document
---
## https://github.com/rubenarslan/codebook

## Generate markdown codebooks from the attributes of the variables in  data frame
```{r setup}
knitr::opts_chunk$set(
  warning = TRUE, # show warnings during codebook generation
  message = TRUE, # show messages during codebook generation
  error = TRUE, # do not interrupt codebook generation in case of errors,
                # usually makes debugging easier, and sometimes half a codebook
                # is better than none
  echo = FALSE  # don't show the R code
)
ggplot2::theme_set(ggplot2::theme_bw())

pander::panderOptions("table.split.table", Inf)

load("C:/Users/tingtinf/Downloads/t1.RData") 
codebook_data = t1
```

##Sometimes, the metadata is not set up in such a way that codebook can leverage it fully. These functions help fix this.

```{r codebook}
library(codebook) # load the package
# omit the following lines, if your missing values are already properly labelled
codebook_data <- detect_missing(codebook_data,
    only_labelled = TRUE, # only labelled values are autodetected as
                                   # missing
    negative_values_are_missing = FALSE, # negative values are NOT missing values
    ninety_nine_problems = TRUE,   # 99/999 are missing values, if they
                                   # are more than 5 MAD from the median
    )
```

# If you are not using formr, the codebook package needs to guess which items
# form a scale. The following line finds item aggregates with names like this:
# scale = scale_1 + scale_2R + scale_3R
# identifying these aggregates allows the codebook function to
# automatically compute reliabilities.
# However, it will not reverse items automatically.


```{r}
codebook_data <- detect_scales(codebook_data)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

#generating a codebook is as simple as calling codebook from a chunk in an rmarkdown document.
```{r}
codebook(codebook_data)
```
